A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-10-29 paper/elsarticle/elsarticle-template.tex
paper

While interest in spatial AR in industrial settings has been growing, its deployment in industrial settings remains well behind that of wearable AR systems such as handhelds or head-mounted displays. One of the main shortcomings of typical projector-based spatial AR relative to AR relying on wearables is the applicability of spatial AR only to augmenting scenes within the projector's own static field of view. Here, dynamic projection systems---using mirror heads to deflect the projection across wider areas---has the potential to bridge the gap to wider industrial penetration. Yet the increase in the area to be covered comes with noteworthy challenges in terms of ensuring that the images to be projected appear free of distortions to the users. Considering a planar surface to be augmented (e.g., a floor, wall, or table), unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular, but will instead be subject to projective distortions. Such distortions can be corrected for by carrying out a cumbersome manual process referred to as keystone correction---involving warping an image by perturbing its corners until the desired effect is produced when projected to the scene---to appropriately warp the image to be projected, often using software bundled with the projector. Automating this manual, time-consuming, and error-prone process significantly reduces the time needed for the industrial engineering of a spatial AR application and therefore has potential to promote adoption by industry. Especially manufacturing processes of large products that remain at a static mounting position during the assembly process---i.e., industrial site assembly---offer a significant application potential for the use of spatial AR as part of worker assistance systems \cite{mayrhofer2019one}.

Our contribution is to propose a wide-area spatial AR system for planar scenes that produces the effect of keystone correction analytically, free of any manual interaction. Most importantly, we do this in a manner placing the axes of the augmentation in accordance with the axes of a camera placed to face directly towards the scene plane (a camera we shall in what follows refer to as `downwards facing', for brevity). This facilitates placement of augmentations, since establishing the principal axes of the augmentation thus reduces to placing the downwards-facing camera in a manner such that the $X$- and $Y$-axes of the image align with the intended $X$- and $Y$-axes of the augmentation. We achieve this by warping the image to be projected using a plane-induced homography computed to produce the effect of projecting the image not from the actual projector viewpoint, but in accordance with the viewpoint of a \textit{virtual} projector. We place this virtual projector to (i) face directly downwards to the target location in the scene plane and (ii) rotate its axes in accordance with those of the camera. Moreover, our system enables specifying the dimensions of augmentations in metric terms, which we achieve by placing the virtual projector at the appropriate height above the scene plane. Finally, our system set up to handle a projector equipped with a steerable mirror (without need for explicitly modeling the action of the steerable mirror on the projector), thereby enabling wide-area applications exceeding the immediate field of view of the projector without needing to rely on multiple projectors.

@@

If the projector is calibrated and its pose relative to the scene plane is known, a `virtual' projector (with the same calibration $\mathtt{K}$ and lens distortion model coefficients) can be placed elsewhere relative to the scene plane. If we for a moment imagine that the projector---at its recovered pose---functions as a camera,\footnote{Recall that the calibration matrix~$\mathtt{K}$ enables computing (i) the projection of a scene point to the image plane (the function of a camera), or (ii) the back-projection of a pixel in the image plane, giving a ray into the scene (along which a projector illuminates the scene with the given pixel).} then (i) projecting an image to the scene plane \textit{from the viewpoint of the virtual projector} and (ii) acquiring the resulting projected image \textit{from the viewpoint of the recovered projector} gives the desired corrective warp. Projecting an image warped in this manner to the scene plane from the viewpoint of the recovered projector then has the same effect as projecting the original image to the scene plane from the viewpoint of the virtual projector. This warp can be effected using a plane-induced homography, computed analytically as a function of the scene plane, the projector, and the virtual projector.

@@

\begin{figure}
    \centering
    \subfloat[\centering Original image.]{{\includegraphics[height=3.4cm]{images/projim.png}}}
    \qquad
    \subfloat[\centering Projecting the original image (downwards view).]{{\includegraphics[height=3.4cm]{images/proj_projim.png}}}
    \caption{Projection to the scene plane from the viewpoint of the recovered projector (bottom left, black; virtual projector in center, gray) for a given target location. (a) Original image. (b) Projecting the original image to the scene plane introduces projective distortions if the projector is not fronto-parallel with the scene plane, as is the case here.}
    \label{fig:proj}
\end{figure}

\begin{figure}
    \centering
    \subfloat[\centering Our warped image.]{{\includegraphics[height=3.4cm]{images/projim_warped_scaled.png}}}
    \qquad
    \subfloat[\centering Projecting our warped image (downwards view).]{{\includegraphics[height=3.4cm]{images/proj_projim_waped.png}}}
    \caption{Projection to the scene plane from the viewpoint of the recovered projector (bottom left, black; virtual projector in center, gray) for a given target location. (a) Original image warped using our approach. (b) After warping the original image according to our approach for the given target location, the image is projected with the effect of projecting the original image from the viewpoint of the virtual projector. This renders the projection free of projective distortions, aligned with the axes of the virtual camera, and at the desired metric scale. Note that pixels shown in black will in effect be ignored by the projector.}
    \label{fig:warp}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat[\centering Hardware setup (projector, steerable mirror system, camera).]{{\includegraphics[height=3.3cm]{images/system2.pdf}}}
    \quad
    \subfloat[\centering Projection of warped image from Figure~\ref{fig:warp}(a) to corresponding target location.]{{\includegraphics[height=3.3cm]{images/hans_undist.pdf}}}
    \caption{Evaluation scenario. (a) Our hardware setup, comprised of a Panasonic PT-RZ660BE projector, a steerable mirror system manufactured by Dynamic Projection Institute, and a Stereolabs Zed 2 stereo camera, of which we used only the left view. (b) Example augmentation produced by projecting---to one of our 15 target locations across the floorspace---an image warped using our approach, as seen from the downwards-facing camera. Note that the warp places the axes of the augmentation in accordance with the axes of the camera, and that the dimensions of the augmentation are in line with the desired target dimensions (50~cm~$\times$~31.25~cm). Corners of the full projected image extent projected to the floor in light green (emphasized with overlain dashed circles).}
    \label{fig:eval}
\end{figure}

>>>>

\begin{figure}
    \centering
    \subfloat[\centering Original image.]{{\includegraphics[height=3.4cm]{images/projim.png}}}
    \qquad
    \subfloat[\centering Projecting the original image (downwards view).]{{\includegraphics[height=3.4cm]{images/proj_projim.png}}}
    \caption{Projection to the scene plane from the viewpoint of the recovered projector, facing a given target location. (a) Original image. (b) Projecting the original image from the viewpoint of the recovered projector (bottom left, black) to the scene plane introduces projective distortions if the projector is not fronto-parallel with the scene plane, as is the case here.}
    \label{fig:proj}
\end{figure}

While interest in spatial AR in industrial settings has been growing, its deployment in industrial settings remains well behind that of wearable AR systems such as handhelds or head-mounted displays. One of the main shortcomings of typical projector-based spatial AR relative to AR relying on wearables is the applicability of spatial AR only to augmenting scenes within the projector's own static field of view. Here, dynamic projection systems---using mirror heads to deflect the projection across wider areas---has the potential to bridge the gap to wider industrial penetration. Yet the increase in the area to be covered comes with noteworthy challenges in terms of ensuring that the images to be projected appear free of distortions to the users. Considering a planar surface to be augmented (e.g., a floor, wall, or table), unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular, but will instead be subject to projective distortions (cf.\ Figure~\ref{fig:proj}). Such distortions can be corrected for by carrying out a cumbersome manual process referred to as keystone correction---involving warping an image by perturbing its corners until the desired effect is produced when projected to the scene---to appropriately warp the image to be projected, often using software bundled with the projector. Automating this manual, time-consuming, and error-prone process significantly reduces the time needed for the industrial engineering of a spatial AR application and therefore has potential to promote adoption by industry. Especially manufacturing processes of large products that remain at a static mounting position during the assembly process---i.e., industrial site assembly---offer a significant application potential for the use of spatial AR as part of worker assistance systems \cite{mayrhofer2019one}.

\begin{figure}
    \centering
    \subfloat[\centering Our warped image.]{{\includegraphics[height=3.4cm]{images/projim_warped_scaled.png}}}
    \qquad
    \subfloat[\centering Projecting our warped image (downwards view).]{{\includegraphics[height=3.4cm]{images/proj_projim_waped.png}}}
    \caption{Projection to the scene plane from the viewpoint of the recovered projector for a given target location. (a) Original image warped using our approach. (b) After warping the original image according to our approach for the given target location, the image is projected from the viewpoint of the recovered projector (bottom left, black) with the effect of projecting the original image from the viewpoint of the virtual projector (center, gray). This renders the projection free of projective distortions, aligned with the axes of the virtual camera, and at the desired metric scale. Note that black pixels will in effect be ignored by the projector.}
    \label{fig:warp}
\end{figure}

Our contribution is to propose a wide-area spatial AR system for planar scenes that produces the effect of keystone correction analytically, free of any manual interaction. Most importantly, we do this in a manner placing the axes of the augmentation in accordance with the axes of a camera placed to face directly towards the scene plane (a camera we shall in what follows refer to as `downwards facing', for brevity). This facilitates placement of augmentations, since establishing the principal axes of the augmentation thus reduces to placing the downwards-facing camera in a manner such that the $X$- and $Y$-axes of the image align with the intended $X$- and $Y$-axes of the augmentation. We achieve this by warping the image to be projected using a plane-induced homography computed to produce the effect of projecting the image not from the actual projector viewpoint, but in accordance with the viewpoint of a \textit{virtual} projector (cf.\ Figure~\ref{fig:warp}). We place this virtual projector to (i) face directly downwards to the target location in the scene plane and (ii) rotate its axes in accordance with those of the camera. Moreover, our system enables specifying the dimensions of augmentations in metric terms, which we achieve by placing the virtual projector at the appropriate height above the scene plane. Finally, our system set up to handle a projector equipped with a steerable mirror (without need for explicitly modeling the action of the steerable mirror on the projector), thereby enabling wide-area applications exceeding the immediate field of view of the projector without needing to rely on multiple projectors.

@@

If the projector is calibrated and its pose relative to the scene plane is known, a `virtual' projector (with the same calibration $\mathtt{K}$ and lens distortion model coefficients) can be placed elsewhere relative to the scene plane. If we for a moment imagine that the projector---at its recovered pose---functions as a camera,\footnote{Recall that the calibration matrix~$\mathtt{K}$ enables computing (i) the projection of a scene point to the image plane (the function of a camera), or (ii) the back-projection of a pixel in the image plane, giving a ray into the scene (along which a projector illuminates the scene with the given pixel).} then (i) projecting an image to the scene plane \textit{from the viewpoint of the virtual projector} and (ii) acquiring the resulting projected image \textit{from the viewpoint of the recovered projector} gives the desired corrective warp (cf.\ Figure~\ref{fig:warp}). Projecting an image warped in this manner to the scene plane from the viewpoint of the recovered projector then has the same effect as projecting the original image to the scene plane from the viewpoint of the virtual projector. This warp can be effected using a plane-induced homography, computed analytically as a function of the scene plane, the projector, and the virtual projector.

@@

@@

\begin{figure}
    \centering
    \subfloat[\centering Hardware setup (projector, steerable mirror system, camera).]{{\includegraphics[height=3.35cm]{images/system2.pdf}}}
    \quad
    \subfloat[\centering Projection of warped image from Figure~\ref{fig:warp}(a) to corresponding target location.]{{\includegraphics[height=3.35cm]{images/hans_undist.pdf}}}
    \caption{Evaluation scenario. (a) Our hardware setup, comprised of a projector, a steerable mirror system, and a stereo camera, of which we used only the left view. (b) Example augmentation produced by projecting---to one of our 15 target locations across the floorspace---an image warped using our approach, as seen from the downwards-facing camera. Note that the warp places the axes of the augmentation in accordance with the axes of the camera, and that the dimensions of the augmentation are in line with the desired target dimensions (50~cm~$\times$~31.25~cm). Corners of the full projected image extent projected to the floor in light green (emphasized with overlain dashed circles).}
    \label{fig:eval}
\end{figure}
